the rethinking way of doing the binary outcome modeling

### 2021-03-23 scripts/49_16s_stacked_barplot.Rmd
ud[ate

# merge the new no_color_df_full to the original df
dat <- bind_rows(
  no_color_df_full,
  color_group %>% 
    pluck('FALSE')
)   
```

>>>>

# merge the new no_color_df_full to the original df
dat <- bind_rows(
  no_color_df_full,
  color_group %>% 
    pluck('FALSE')
)

dat %>%  write_csv('../data/the_data_to_make_panel_B.csv')
```

### 2021-03-23 scripts/54_rethinking_binary.Rmd
ud[ate

# the std of b is 2, since we assume the microbiome could have big impact on immunology (based on our previous understanding and knowledge )
precis(mtox,  prob = 0.95)
plot(precis(mtox, depth = 2, prob = 0.95) ) 
# there is baseline difference between penn and Msk and MSK has higher tox rage in general.
# it doesn't seem diversity has a clear association with tox rate after correcting for center wise difference
```

@@

>>>>

# the std of b is 2, since we assume the microbiome could have big impact on immunology (based on our previous understanding and knowledge )
precis(mtox,  prob = 0.95)
plot(precis(mtox, depth = 2, prob = 0.95) ) 
# there is baseline difference between penn and Msk and MSK has higher tox rage in general.
# it doesn't seem diversity has a clear association with tox rate after correcting for center wise difference
div_value <- c(-1, 1)
```

@@

```{r}
# combine M and P since they look very similar and also save some space
low_M <- post_tox %>% pluck('m') %>% pluck(1)
low_P <- post_tox %>% pluck('p') %>% pluck(1)
high_M <- post_tox %>% pluck('m') %>% pluck(2)
high_P <- post_tox %>% pluck('p') %>% pluck(2)
low_all <- bind_rows(
  tibble(value = low_M),
  tibble(value = low_P)
) %>% mutate(grp = 'low')

high_all <- bind_rows(
  tibble(value = high_M),
  tibble(value = high_P)
)%>% mutate(grp = 'high')

tox_all <- bind_rows(
  low_all,
  high_all
)

tox_all  %>% 
  gghistogram(x = 'value',bins = 30, fill = 'grp', palette = 'nejm', color = 'white',
                  xlab = 'Predicted probability of toxicity', ylab = 'Probability density',
                  title = '') +
      scale_x_continuous(breaks = seq(0, 1, 0.1)) +
  ggsave('../figs/bayesican_tox_combined.pdf', width = 6, height = 4)
```
